---
title: "Covid91 vaccine study Final2024"
author: "Andy Trejo"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="finalSumr2024.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

## Males
```{r}
require(tidyverse)  # For data manipulation and visualization
require(tigerstats) # For statistical analysis
require(forcats)    # For handling categorical variables (factors)
FinalDat <- read.csv(file="finalSumr2024.csv", header=TRUE)
FinalData <- FinalDat %>% select(-one_of("X"))
FinalData <- FinalData %>%
  mutate(across(where(is.character), as.factor))
```


## Females
```{r}
require(tidyverse)  # For data manipulation and visualization
require(tigerstats) # For statistical analysis
require(forcats)    # For handling categorical variables (factors)
female_data <- FinalData %>% filter(DrugUser == "Female")
```
```{r}
ggplot(female_data, aes(x = DrugUser, y = treatment)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +  # Boxplot with custom colors
  geom_jitter(color = "darkred", alpha = 0.6, width = 0.1) +  # Add data points as jittered red dots
  stat_summary(fun = "mean", geom = "point", shape = 18, size = 3, color = "black", fill = "yellow") +  # Add mean points
  stat_summary(fun = "median", geom = "point", shape = 17, size = 3, color = "black", fill = "green") +  # Add median points
  labs(title = "Vaccine Effectiveness for Females", 
       x = "DrugUser", 
       y = "treatment") +
  theme_minimal()
```






## LGBTQ



## Druggies


# Overall Results and Conclusions